A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-13 paper/supplement.tex
Edits to supplement.  Think about adding a folder to the Git Repo with Supplemental Material.

\item Put R Stan code here

@@

\pagebreak
\section{Posterior predictive graphical checks}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-1.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-2}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-3.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-4.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-5.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-6.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-7.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-8.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-9.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-10.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-11.pdf}
\end{figure}
\clearpage

>>>>

\item Stan code for Model 4, estimated using the Backblaze data set (also available as a supplementary .csv file).

@@

\pagebreak
\section{Posterior predictive graphical checks}
\item Full set of Figures 5 and 6 for all 44 drive-models.  Numbering in the top left indicates drive-model.  Left: Adjusted K-M estimates of the proportion failing.  The original data (bold line) and 19 ``replicated" data sets from the posterior predictive distribution (dashed lines) are shown.  Right: Posterior median of proportion failing as a function of time for Models 1-4.  Plotted on Weibull probability scales.  The solid step function is the adjusted K-M estimate.  
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-1.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-2}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-3.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-4.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-5.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-6.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-7.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-8.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-9.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-10.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-11.pdf}
\end{figure}
\clearpage
